Formalization, Mechanization and Automation of \\ G\"{o}del's Proof of God's Existence\thanks{This work has been supported by the German Research Foundation under grant BE2501/9-1.}

### 2017-09-01 Papers/2013/ArXiv/GodProof-Abstract.tex
Fix bibliography

\noindent
\textbf{Update (31/08/2017):} The abstract below, uploaded to arXiv on
21/08/2013, was the first communication of the computer-assisted
formalization of G\"odel's ontological proof. Since then, the
following longer papers have been published:
%\cite{B39,B40,B45,B47,B49,B52,B56,B57,B60,B61,B62,B63,B64,B65,B66}.
\cite{W50,J28,B15,C39,C40,C41,C42,C44,C46,C52,W55,J32,C55,C60,B16,B66,,J35,J36,C65}.

@@

\noindent
Scott's version of G\"{o}del's proof has now been 
analysed for the first-time
with an unprecedent degree of detail 
and formality with the help of theorem provers; cf.~\cite{FormalTheologyRepository}. 
The following has been done (and in this order):
\begin{itemize}
\item A detailed natural deduction proof.
%
\item A formalization of the axioms, definitions and theorems in the TPTP THF syntax \cite{J22}.
%
\item Automatic verification of the consistency of the axioms and 
definitions with Nitpick \cite{Nitpick}.
%
\item Automatic demonstration of the theorems with the provers LEO-II \cite{LEO-II} and Satallax \cite{Satallax}.

>>>>

\noindent
\textbf{Update (31/08/2017):} The abstract below, uploaded to arXiv on
21/08/2013, was the first communication of the computer-assisted
formalization of G\"odel's ontological proof. Since then, the
following longer papers have been published:
%\cite{B39,B40,B45,B47,B49,B52,B56,B57,B60,B61,B62,B63,B64,B65,B66}.
\cite{W50,J28,B15,C39,C40,C41,C42,C44,C46,C52,W55,J32,C55,C60,B16,B66,J35,J36,C65}.

@@

\noindent
Scott's version of G\"{o}del's proof has now been 
analysed for the first-time
with an unprecedent degree of detail 
and formality with the help of theorem provers; cf.~\cite{FormalTheologyRepository,ComputationalPhilosophyRepository}. 
The following has been done (and in this order):
\begin{itemize}
\item A detailed natural deduction proof.
%
\item A formalization of the axioms, definitions and theorems in the TPTP THF syntax \cite{J22}.
%
\item Automatic verification of the consistency of the axioms and 
definitions with Nitpick \cite{Nitpick}.
%
\item Automatic demonstration of the theorems with the provers LEO-II \cite{LEO-II} and Satallax \cite{Satallax}.
